Full Title of Article\titlebreak This Title Has A Line Break

### 2021-08-18 Submission/Paper/ML4H/Paper.tex
changed keyword table to appendix

\begin{abstract}
\tab Dementia is a neurodegenerative disorder that causes cognitive decline and affects more than 50 million people worldwide. Dementia is under-diagnosed by healthcare professionals—only one in four people who suffer from dementia are diagnosed. Even when a diagnosis is made, it may not be entered as a structured diagnosis code in a patient’s charts.  Information relevant to cognitive impairment is often found within electronic health records but manual review of clinician notes by experts is both time consuming and often prone to errors. Automated evaluation of these notes presents an opportunity to label patients with cognitive impairment (CI) in real-world data. 
\end{abstract}
\begin{keywords}
EHR, NLP, Demetia
\end{keywords}

@@

\paragraph{Preprocessing}
\label{sec:Preprocessing} For each patient in our gold-standard dataset, we extracted unstructured clinician notes, identified matches to dementia-related keywords (listed in Table 1), and constructed 800 character sequences from the note text around each of these matches. Our cohort of 16,428 patients had 279,224 sequences in total.

\begin{table*}[htbp]
\floatconts
  {tab:operatornames}
  {\caption{Keywords indicative of Cognitive Impairment}}%
    {
        \begin{tabular}{lcc}
            \toprule
            \bfseries Keyword & \bfseries Match Count \\
            \midrule

            \bottomrule
        \end{tabular}
    }
\end{table*}

@@

The final dataset was split between train (95\%) and holdout test (5\%) sets, stratified across label and proportion of sequences annotated manually and through always patterns. % {Will change} % 
Validation datasets were split from the train set using techniques described in the Methodology section. Table 2 shows demographics of the cohort of patients.  
\section{Methodology}
\label{sec:Methodology}

@@

\label{sec:BaselineTFIDF}  
\paragraph{(3) Model 1 + Model 2} % {TBD} %

@@

@@

>>>>

\begin{abstract}
\tab Dementia is a neurodegenerative disorder that causes cognitive decline and affects more than 50 million people worldwide. Dementia is under-diagnosed by healthcare professionals—only one in four people who suffer from dementia are diagnosed. Even when a diagnosis is made, it may not be entered as a structured diagnosis code in a patient’s charts.  Information relevant to cognitive impairment is often found within electronic health records but manual review of clinician notes by experts is both time consuming and often prone to errors. Automated evaluation of these notes presents an opportunity to label patients with cognitive impairment (CI) in real-world data. 
\end{abstract}

\begin{keywords}
EHR, NLP, Demetia
\end{keywords}

@@

\paragraph{Preprocessing}
\label{sec:Preprocessing} For each patient in our gold-standard dataset, we extracted unstructured clinician notes, identified matches to dementia-related keywords (Appendix B), and constructed 800 character sequences from the note text around each of these matches. Our cohort of 16,428 patients had 279,224 sequences in total.

@@

The final dataset was split between train (95\%) and holdout test (5\%) sets, stratified across label and proportion of sequences annotated manually and through always patterns. % {Will change} % 
Validation datasets were split from the train set using techniques described in the Methodology section. Table 2 shows demographics of the cohort of patients.

\section{Methodology}
\label{sec:Methodology}

@@

\label{sec:Baseline+TFIDF}  
\paragraph{(3) Model 1 + Model 2} % {TBD} %

@@

% binary classification model stats - probability threshold of 0.89
\begin{table*}[hbtp]
%   {\caption{TF-IDF Vector Features Correlation}}
  {\begin{tabular}{lccccccc}
    \toprule

    \bfseries Model & \bfseries AUCROC & \bfseries ACC & \bfseries Sensitivity & \bfseries Specificity & \bfseries FP & \bfseries FN & \bfseries Prediction Threshold \\ 
    Model 2 & 0.94 & 0.90 & 0.73 & 0.94 & __ & __ & 0.89 \\

    \bottomrule
  \end{tabular}}

\end{table*}

@@

% Talk about Stats
% TF-IDF model struggles with understanding context of words around keyword match

We evaluated each model using a prediction threshold to maximize the accuracy and calculated performance metrics based on that threshold. Model performance for each model in shown in Table 2.

\section{Conclusion and Future Work} 
\label{sec:ConclusionFutureWork} We applied innovative Machine Learning and Deep Learning NLP techniques to identify patients with CI in EHR. Our work can help combat the issues of underdiagnosis and misdiagnosis for dementia.

Future plans include reducing false positives by gathering more annotated sequences and using deep learning natural language. Currently, many of our false positives are from the model identifying the presence of a keyword but struggling to understand the context around the keyword match; many of these contexts negate the presence of CI for the patient in question. Deep Learning can leverage contextual information, making it promising for this task.

\clearpage
\appendix

% Appendix A
\section{UI of Annotation Tool}
Placeholder

% Appendix B
\section{Keywords} % wi
\begin{table}[hbtp] 
\floatconts  
{tab:operatornames}
    {\caption{Keywords indicative of Cognitive Impairment}} \\
    {
        \begin{tabular}{lccc}
        \toprule
        \bfseries Keyword & \bfseries Match Count\\
        \midrule

        \bottomrule
        \end{tabular}
    }
\end{table}
